Marlowe: implementing and analysing financial contracts on blockchain

### 2019-12-09 papers/marlowe2019/paper.tex
Added cross reference to sectino 4 to intro.
Weaken timeout precondition

\DeclareUnicodeCharacter{21D2}{$\Rightarrow$}
\DeclareUnicodeCharacter{2227}{$\wedge$}
\DeclareUnicodeCharacter{2260}{$\neq$}
\DeclareUnicodeCharacter{2265}{$\geq$}
\DeclareUnicodeCharacter{2264}{$\leq$}
\DeclareUnicodeCharacter{27F9}{$\Longrightarrow$}
\DeclareUnicodeCharacter{2987}{$\llparenthesis$}
\DeclareUnicodeCharacter{2988}{$\rrparenthesis$}

@@

Because Marlowe is a DSL, we are able to build special purpose tools and techniques to support it. Crucially in a financial environment we are able to \emph{exhaustively analyse contracts} without executing them, so that we can, for instance, check whether any particular contract makes all the payments it should: in the case it does not, we get an explicit example of how it can fail. This analysis is built into the Marlowe Playground. We are also able to use program verification techniques to prove guarantees about the implementation of Marlowe, including a guarantee that ``money in $=$ money out'' for all contracts.

@@

\begin{verbatim}
theorem timedOutTransaction_closes_contract :
"validAndPositive_state sta
 ⟹ iniSlot ≥ minSlot sta
 ⟹ iniSlot ≥ maxTimeContract cont
 ⟹ endSlot ≥ iniSlot
 ⟹ accounts sta ≠ []
 ⟹ isClosedAndEmpty
         (computeTransaction ⦇ interval = (iniSlot, endSlot)
                             , inputs = [] ⦈ sta cont)"
\end{verbatim}

>>>>

\DeclareUnicodeCharacter{21D2}{$\Rightarrow$}
\DeclareUnicodeCharacter{2227}{$\land$}
\DeclareUnicodeCharacter{2228}{$\lor$}
\DeclareUnicodeCharacter{2260}{$\neq$}
\DeclareUnicodeCharacter{2265}{$\geq$}
\DeclareUnicodeCharacter{2264}{$\leq$}
\DeclareUnicodeCharacter{27F9}{$\Longrightarrow$}
\DeclareUnicodeCharacter{2987}{$\llparenthesis$}
\DeclareUnicodeCharacter{2988}{$\rrparenthesis$}

@@

Because Marlowe is a DSL, we are able to build special purpose tools and techniques to support it. Crucially in a financial environment we are able to \emph{exhaustively analyse contracts} without executing them, so that we can, for instance, check whether any particular contract makes all the payments it should: in the case it does not, we get an explicit example of how it can fail. This analysis is built into the Marlowe Playground. We are also able to use program verification techniques to prove guarantees about the implementation of Marlowe, including a guarantee that ``money in $=$ money out'' for all contracts. Section \ref{sec:analysis} covers analysis and verification.

@@

\begin{verbatim}
theorem timedOutTransaction_closes_contract :
"validAndPositive_state sta
 ⟹ iniSlot ≥ minSlot sta
 ⟹ iniSlot ≥ maxTimeContract cont
 ⟹ endSlot ≥ iniSlot
 ⟹ accounts sta ≠ [] ∨ cont ≠ Close
 ⟹ isClosedAndEmpty
         (computeTransaction ⦇ interval = (iniSlot, endSlot)
                             , inputs = [] ⦈ sta cont)"
\end{verbatim}
